\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
%Last year’s classification team described our portion of the project in terms of three main goals to accomplish with the tweets and web pages given to us. First we will find the best way to extract information that will be used for document representation. Next, the best feature selection method to construct feature vectors. And finally, the best way to classify each document into categories, considering the ontology developed in the IDEAL project. The team last year researched various methods and tools that could be used to accomplish these goals, and ended up with a system that was able to accomplish these goals with a promising degree of success. This year, we will expand upon their work and try to improve upon their successes. We will explore the technologies and techniques that they utilized, as well as potential new and improved technologies, and attempt to optimize their system to work with a larger library of tweets and web pages.

In the grand scheme of a large Information Retrieval project, the work of our team will be that of performing text classification on both the tweet collections and their associated web pages. In order to accomplish this task, we will seek to complete three primary goals. We will begin by performing research to determine the best way to extract information that will be used to represent a given document. Following that, we will work to determine the best method to select features and then construct feature vectors. Our final goal is to use the information gathered previously to build an effective way to classify each document in the tweet and web page collections. We intend for these classifiers to be built with consideration to the ontology developed for the IDEAL project.

The team assigned to perform this classification work last year researched various methods and tools that could be useful in accomplishing the goals we have set forth. Last year's team developed a system that was able to accomplish similar goals to those we have set forth with a promising degree of success. Our goal for this year is to improve upon their successes using new technologies such as Apache Spark in our work. It is our hope that this will allow us to build a more optimized system capable of working with larger collections of tweets and web pages.

\end{abstract}